\documentclass[margin]{res}
\setlength{\textwidth}{5.1in} 

\begin{document}


 \moveleft.5\hoffset\centerline{\large\bf Antony Savio}

 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

 \moveleft.5\hoffset\centerline{C-410, Surabhi Apartments}
 \moveleft.5\hoffset\centerline{Bilekahalli, Bangalore - 560076}

\begin{resume}
 
\section{education} {\sl Bachelor of Technology} \\
		Computer Science and Engineering \\
                SRM University, August 2011 - May 2015 \\
 		G.P.A. 8.48/10.0
 
 \section{experience} 
                {\sl Senior Software Engineer} \hfill September 2018 -\\
                Inspirit IoT, Chennai
                \begin{itemize} \itemsep -2pt
                \item Wrote translators to convert neural network specifications from popular frameworks(Caffe, Tensorflow) into in-house specification.
                \item Developed backend infrastructure in C to perform Neural Network Inference targeting SIMD intrinsics.
                \item Promoted from Software Development Engineer II to Senior Software Engineer in October 2019.
                \item Led successful development of a proof of concept safety product for a major construction company.
                This was built around Object Detection/Segmentation Neural Networks.
                \item Developed major components of Inspirit's Facial Recognition Product.
                \begin{itemize} \itemsep -2pt
                \item Primary components were Facial Detection/Recognition Neural Networks.
                \item All components were written in modern C++.
                \end{itemize}
                \end{itemize}

                {\sl Analyst - I} \hfill July 2015 - August 2018\\
                Engineering Software Development,\\
                Caterpillar Inc., Chennai 
                 \begin{itemize}  \itemsep -2pt 
                 \item Involved in development of 2 in-house analysis software. 
                 \item Was involved in a re-architecture project aimed to rewrite existing software targeting cross-platform capabilities, high performance and low memory overhead.
                 \item Complete ownership of development, maintenance and test for cross platform C++ libraries for 2D Rendering(Using OpenGL) and Multithreaded IO for Time series data(using HDF5).
                 \item Was promoted to Analyst - I from Assistant Analyst in July of 2017.
                \end{itemize}
                
        
		
\section{tools/skills}  C++, C, Python, Git, OpenGL, Bash\\
                        Object Oriented Design, Parallel Programming
            
\section{contact}
	   {\sl Primary :}
	   +91-999 468 3101 \\
	   {\sl Alternate :}
	   +91-990 029 5542 \\
	   {\sl Email :}
	   antonysavio93@yahoo.co.in \\
	   {\sl LinkedIn :}
	   https://in.linkedin.com/in/antony-savio-8973a2107 \\ 

\end{resume}
\end{document}




